\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-08 paper/main.tex
remove parts regarding descriptive nouns

    \caption{Narrator's descriptive nouns. All categories sorted alphapetically. Examples are given in English. Description (of rules) fehlt in dieser Tabelle (vgl. alte Tabelle auf der allerletzten Seite). Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng. Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.}
\label{tab:descr-nouns}
\begin{tabular}{lllllllllll}
\textbf{label} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
body & back, hip, shoulder; jacket, dress, shirt & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII \tabularnewline
bodypart  & arm, finger, leg, toe & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII\tabularnewline
face & face, ear, nose, mouth & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII \tabularnewline
female & nurse, mother, woman & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII \tabularnewline
females & women & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII \tabularnewline
fname & Jenny & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII \tabularnewline
furniture & bench, bed, table, chair & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII \tabularnewline
geo & building, tree, street, alley, meadow, cornfield, river & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII \tabularnewline
geo-room & living room; wall, door, window, floor, turf & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII \tabularnewline
head & head, hair, ear, neck, helmet & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII \tabularnewline
male & man, father, soldier & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII \tabularnewline
males & boys, opponents & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII \tabularnewline
mname & Bubba, Kennedy & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII \tabularnewline
object & telephone, car & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII \tabularnewline
objects & wheels, photos & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII \tabularnewline
persons & hippies, patients & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII \tabularnewline
setting\_new & on a ``bridge'', on an ``alley'', on ``campus'' & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII \tabularnewline
setting\_rec & at the ``bus stop'' & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII \tabularnewline
++ &  in the ``evening'', it's ``daytime'', ``later'' & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII \tabularnewline

@@

% new; not from haeusler2016annotation
Because naturalistic stimuli are multi-dimensional and their temporal structure
is (usually) unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. Nevertheless, theory-driven analyses like a general
linear model (GLM) are necessary to not just explain how but also when and why a
brain region is responding to a stimulus \citep{hamilton2018revolution}. Studies
using GLMs based on annotations of a stimulus' temporal structure have
elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.

% adapted from haeusler2016annotation
% nun ja, folgend nicht super korrekt: sentences sind nicht vollständige
% Sätze im linguistischen Sinne (Subjekt, Objekt, Prädikat), sondern auch
% Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh").
% Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am
% Ende gekennzeichnet. Sollte aber so passen.
For this publication, we annotated the onsets and offsets, and content of
sentences, single words, and phonemes spoken in the movie Forrest Gump (R.
Zemeckis, Paramount Pictures, 1994) \citep{ForrestGumpMovie}. fMRI data of
participants watching the audio-visual movie \citep{hanke2016simultaneous} and
it's audio-description for visually impaired persons \citep{hanke2014audiomovie}
are the core data of the publicly available \textit{studyforrest} dataset
(\href{www.studyforrest.org}{studyforrest.org}). Additional fMRI data
\citep{sengupta2016extension} include retinotopic mappings and localization of
higher visual areas of the same participants.
% paper regarding mention musical not mentioned
% und damit zitiere ich mich als dortiger Coauthor nicht selbst. Skandal!

The current annotation facilitates modelling of hemodynamic brain responses
correlating with speech-related events in the movie and audio-description.
Further, it extends already available annotations of portrayed emotions
\citep{labs2015portrayed} and perceived emtions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}. All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional
confound measures describing key properties of major building blocks of the stimulus.

\section*{Materials and methods}
\subsection*{Stimulus}
% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
% “hardcoded” Zitationen sind aber noch im laufenden Text.
We annotated speech in the slightly shortened ``research cut'' of the movie
\citep{hanke2016simultaneous} and its temporally aligned audio-description
\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
movie's audio-description that was broadcast as an additional audio track for
visually impaired listeners on Swiss public television (Koop, Michalski,
Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
off-screen voice of the main character Forrest Gump. In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
\subsection*{Annotation procedure}
% wo kommen die "preliminaries transcriptions" her?
% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
non-speech vocalizations (e.g. laughing or groaning;
non\_speech\_vocalization.json), and the audio-description's narrator
(german\_audio\_description.csv) were merged and converted to Praat's
\citep{boersma2019praat} .TextGrid format (
\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
containing one onset and offset for usually a couple of sentences was opened
along (the audio file of) the audio-description in Praat v6.0.22 for manual
improvements: In several passes, the approximate temporal onsets and offsets
were corrected. Intervals containing several sentences were split into intervals
containing only one sentence. When two or more persons were speaking
simultaneously the less dominant (background) voice was dropped. Low volume
background speech (especially occurring during music or continuous environmental
noise) or low volume non-speech vocalizations that are difficult to recognize by
a regular audience were dropped, too.

% Alignment preparations
We used the Montreal Forced Aligner v1.0.1
\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal};to
algorithmically identify the onset and offset of each word and phoneme embedded
in the transcribed sentences. To enable the aligner to look up the pronunciation
of every word, we chose a German pronunciation dictionary
\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}
provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses
the Prosodylab PhoneSet. The dictionary was manually updated with movie-specific
German words. The pronunciation of English words occurring in the otherwise
German audio track was taken from an English pronunciation dictionary
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.

@@

% NLP
To automatically analyze linguistic features of words in their corresponding
sentence, we employed the Python package spaCy v2.2.1
(\href{https://spacy.io}{spacy.io}) and a German language model
(de\_core\_news\_md; \href{https://spacy.io/models/de}{spacy.io/models/de})
trained on the TIGER Treebank corpus
(\href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}). We performed
analyses regarding part of speech (i.e. grammatical tagging or word-category
disambiguation), syntactic dependency, lemmatization, word embedding (i.e.
semantic similarity), and if the word is one of the most common words of the
German language. Results of these analyzes were added to the annotation and
saved as .TextGrid file. This .TextGrid file was converted via python script to
a tab separated file in accordance with the brain imaging data structure
(\href{https://bids.neuroimaging.io/}{BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
% BIDS stuff runter zu "Dataset content"?

\subsection*{Data Legend}
% wo wurde automatisch korrigiert (e.g. NE/NN, NONSPEECH)
% s. dictionaries oben in add_part-of-speech-tagging2textgrid.py

\subsubsection*{Start (\texttt{start})}
the onset of the sentences, word or phoneme provided in seconds of stimulus onset.

\subsubsection*{Duration (\texttt{end})}
the duration of the sentences, word or phoneme provided in seconds.

@@

\subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger}(s. table \ref{tab:tag}) which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.

\subsubsection*{Syntactic dependency (\texttt{dep})}
A word's column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
"arc label;word's head;word's child1, word's child2, ..." where the "arc label" (s. table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".

@@

\subsubsection*{Common Word (\texttt{stop})}
For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language ("True") or not ('"False")?

\subsubsection*{Narrator's descriptive nouns (\texttt{descr})}
A categorizing of nouns that serve as auditory cues about the movie's visual content. Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).

@@

Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (conjunctions) lead to increased activation in congruent brain areas.

@@

Software Library)\citep{smith2004fsl}. Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrek ist]. A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.

@@

 based on information drawn from the annotation. The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word. The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll). The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll).

@@

A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech. Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no-speech condition (s. anno2events-files.py). A length of 0.07s was chosen for these events matching the average length of phonemes.
Two regressors reflecting auditory (low-level) features (left-right loudness/volume/amplitude difference; root mean squared amplitude) aligned to the frame rate of (40 ms) were modelled to reduce nuisance effects.
Hier (und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function. Temporal derivatives were also included in the design matrix, and it was subjected to the same temporal filtering as the BOLD time series. Finally, six motion parameters were used as additional nuisance regressors.
The following six t-contrasts were defined: 1) words (21 tag-related regressors) > no-speech; 2) no-speech > all 21 tag-related regressors; 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns. The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].

@@

% results
% von Interpretation klar(er) getrennt halten
Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (all 21 tag-related regressors > no-speech) shows\dots;
left lateralization (bigger cluster left in BA XY => Broca)
The contrasts proper nouns > coordinate conjunctions and proper nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.

>>>>

@@

% new; not from haeusler2016annotation
Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. Nevertheless, theory-driven analyses like a general
linear model (GLM) are necessary to not just explain how but also when and why a
brain region is responding to a stimulus \citep{hamilton2018revolution}. Studies
using GLMs based on annotations of a stimulus' temporal structure have
elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.

% adapted from haeusler2016annotation
% nun ja, folgend nicht super korrekt: sentences sind nicht vollständige
% Sätze im linguistischen Sinne (Subjekt, Objekt, Prädikat), sondern auch
% Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh").
% Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am
% Ende gekennzeichnet. Sollte aber so passen.
For this publication, we annotated the onsets and offsets, and content of
sentences, single words, and phonemes spoken in the movie Forrest Gump (R.
Zemeckis, Paramount Pictures, 1994) \citep{ForrestGumpMovie} and its corresponding audio-description for visually impaired persons. fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie}
are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}). Additional fMRI data include retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
% paper regarding mention musical not mentioned
% und damit zitiere ich mich als dortiger Coauthor nicht selbst. Skandal!

The current annotation facilitates modelling of hemodynamic brain responses
correlating with speech-related events in the two stimuli. Further, it extends already available annotations of portrayed emotions \citep{labs2015portrayed} and perceived emtions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}. All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.

\section*{Materials and methods}
\subsection*{Stimulus}
% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
% “hardcoded” Zitationen sind aber noch im laufenden Text.
We annotated speech in the slightly shortened ``research cut'' of the movie \citep{hanke2016simultaneous} and its temporally aligned audio-description \citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
movie's audio-description that was broadcast as an additional audio track for
visually impaired listeners on Swiss public television (Koop, Michalski Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk 2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
off-screen voice of the main character Forrest Gump. In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
\subsection*{Annotation procedure}
% wo kommen die "preliminaries transcriptions" her?
% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
non-speech vocalizations (e.g. laughing or groaning;
non\_speech\_vocalization.json), and the audio-description's narrator
(german\_audio\_description.csv) were merged and converted to Praat's
\citep{boersma2019praat} .TextGrid format (\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription containing one onset and offset for usually a couple of sentences was opened along (the audio file of) the audio-description in Praat v6.0.22 for manual improvements: In several passes, the approximate temporal onsets and offsets were corrected. Intervals containing several sentences were split into intervals containing only one sentence. When two or more persons were speaking simultaneously the less dominant (background) voice was dropped. Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by a regular audience were dropped, too.

% Alignment preparations
We used the Montreal Forced Aligner v1.0.1
\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal} to algorithmically identify the onset and offset of each word and phoneme embedded
in the transcribed sentences. To enable the aligner to look up the pronunciation
of every word, we chose a German pronunciation dictionary
\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict} provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses the Prosodylab PhoneSet. The dictionary was manually updated with movie-specific German words. The pronunciation of English words occurring in the otherwise German audio track was taken from an English pronunciation dictionary (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.

@@

% NLP
To automatically analyze linguistic features of words in their corresponding
sentence, we employed the Python package spaCy v2.2.1 (\href{https://spacy.io}{spacy.io}) and a German language model (de\_core\_news\_md; \href{https://spacy.io/models/de}{spacy.io/models/de}) trained on the TIGER Treebank corpus (\href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}). We performed analyses regarding part of speech (i.e. grammatical tagging or word-category
disambiguation), syntactic dependency, lemmatization, word embedding (i.e.semantic similarity), and if the word is one of the most common words of the German language. Results of these analyzes were added to the annotation and saved as .TextGrid file. This .TextGrid file was converted via python script to
a tab separated file in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
% BIDS stuff runter zu "Dataset content"?

\subsection*{Data Legend}

\subsubsection*{Start (\texttt{start})}
the onset of the sentence, word or phoneme provided in seconds [ss.milliseconds] of stimulus onset.

\subsubsection*{Duration (\texttt{end})}
the duration of the sentences, word or phoneme provided in seconds [ss.milliseconds].

@@

\subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
For single words, a detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger}(s. table \ref{tab:tag}) which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.

\subsubsection*{Syntactic dependency (\texttt{dep})}
For single words, this column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
"arc label;word's head;word's child1, word's child2, ..." where the "arc label" (s. table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".

@@

\subsubsection*{Common Word (\texttt{stop})}
For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'')?

@@

Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (coordinate conjunctions) lead to increased activation in congruent brain areas.

@@

Software Library)\citep{smith2004fsl}. Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrekt ist]. A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.

@@

 based on information drawn from the annotation. The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word. The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll). The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll) to be used as a nuisance regressors.

@@

A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no audible/comprehensible speech. Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of a sentence or isolated word and to each other onset of the no-speech condition (s. anno2events-files.py). A length of 0.07s was chosen for the events of the no speech regressors  matching the average length of phonemes.
Two regressors reflecting auditory (low-level) features (left-right difference in loudness and root mean squared loudness) aligned to and averaged across the length of every movie frame (40 ms) were modelled to reduce nuisance effects.
Hier (?? und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function. Temporal derivatives were also included in the design matrix. The design was subjected to the same temporal filtering as the BOLD time series. Finally, six motion parameters were used as additional nuisance regressors.
The following six t-contrasts were defined: 1) words (i.e. all 21 tag-related regressors; N=15985) > no-speech; 2) no-speech > words 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns. The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].

@@

% results
% von Interpretation klar(er) getrennt halten
figure \ref{fig:results}
words > no-speech \ref{tab:cope1}
proper nouns > coordinate conjunctions and proper nouns \ref{tab:cope3}
nouns > coordinate conjunctions \ref{tab:cope5}
The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
left lateralization (bigger cluster left in BA XY => Broca)
The contrasts proper nouns > coordinate conjunctions and nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
